Power to the Stimuli: Not the Effect

### 2023-08-21 manuscript_draft.Rmd
figured out trackdown!

Statistical power and power analyses are arguably one of the most important components in planning a research study [@cohen1990]. However, if reviews of transparency and openness in research publications are any clue, the social sciences have failed to fully implement power analyses as part of their common efforts [@hardwicke2020; @doi:10.1177/1745691620979806]. The replication \"crisis\" and credibility revolution have shown that published studies in psychology are underpowered [@opensciencecollaboration2015; @vazire2018]. Pre-registration of a study involves outlining the study and hypotheses before data collection begins [@stewart2020; @d.chambers2014; @nosek2014], and details of a power analyses or other limitations on resources are often used to provide justification for the pre-registered sample quota. Given the combined issues of publish-or-perish and that most non-significant results do not result in published manuscripts, one may expect that power analysis would be especially critical for early career researchers [@rosenthal1979; @simmons2011]. At best, an underpowered study provides limited insight [@halpern2002], and it can be difficult to know if a poorly implemented power analysis is better than no power analysis.

>>>>

```{r trackdown, eval = F}
library(trackdown)
# initial set up 
# upload_file(file = "manuscript_draft.Rmd",
#             gfile = "power2stim_V2_trackdown",
#             gpath = "Studies/PSA007 SPAM-L/Manuscripts/Power",
#             shared_drive = "Psychological Science Accelerator")

# from google 
download_file(file = "manuscript_draft.Rmd", 
            gfile = "power2stim_V2_trackdown",
            gpath = "Studies/PSA007 SPAM-L/Manuscripts/Power",
            shared_drive = "Psychological Science Accelerator")

# to google
update_file(file = "manuscript_draft.Rmd", 
            gfile = "power2stim_V2_trackdown",
            gpath = "Studies/PSA007 SPAM-L/Manuscripts/Power",
            shared_drive = "Psychological Science Accelerator",
            rich_text = TRUE,
            hide_code = TRUE)
```

Statistical power and power analyses are arguably one of the most important components in planning a research study [@cohen1990]. However, if reviews of transparency and openness in research publications are any clue, the social sciences have failed to fully implement power analyses as part of their common efforts [@hardwicke2020; @doi:10.1177/1745691620979806]. The replication "crisis" and credibility revolution have shown that published studies in psychology are underpowered [@opensciencecollaboration2015; @vazire2018]. Pre-registration of a study involves outlining the study and hypotheses before data collection begins [@stewart2020; @d.chambers2014; @nosek2014], and details of a power analyses or other limitations on resources are often used to provide justification for the pre-registered sample quota. Given the combined issues of publish-or-perish and that most non-significant results do not result in published manuscripts, one may expect that power analysis would be especially critical for early career researchers [@rosenthal1979; @simmons2011]. At best, an underpowered study provides limited insight [@halpern2002], and it can be difficult to know if a poorly implemented power analysis is better than no power analysis.
